\documentclass[8pt]{article}

\usepackage{multicol}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=10mm,
 }

\begin{document}
    \title{Kyle Walter Schademan}
    \date{\today}
    \maketitle
\section{Professional summery}\label{sec:int}

A scientist and more than a scientist.  A great soaring curiosity and a strong desire to do productive work.  A belief that advocation and vocation should be one.  Practical implemation of personal beliefs manifested in the following hobbies: Programming Physics and Math simulations in Python, Creating documents in Latex, Using Duoling to learn German (currently 44\% fluent).

\section{Qualifications}\label{sec:int}

    \begin{multicols}{3}
        \begin{itemize}
          \item fast learner
          \item appreciates criticism
          \item independent
          \item kind
          \item curious
          \item determined
          \item enjoys problem solving
          \item self-motivated
          \item consistent
          \item adaptable
        \end{itemize}
    \end{multicols}

\section{Skills}\label{sec:int}

    \begin{multicols}{3}
        \begin{itemize}
          \item \LaTeX coding
          \item C\texttt{++} coding
          \item Python coding
          \item Git repository
          \item Partial differentials
          \item TracePro ray tracing
        \end{itemize}
    \end{multicols}
          

\section{Work History}

Date: July 2014 to present\\
Company: Klein Optical Instruments\\
Description: Optical technician responsible for specification testing, RMA inquires, customer support, quality control, bug checking, prototyping, odd jobs.
\\
\\
Date: August 2012 to December 2013\\
University: Washington State University\\
Description: Dance instructor responsible for teaching introductory and advanced concepts of social dancing.
\\
\\
Date: August 2013 to May 2014\\
University: Washington State University\\
Description: Lab Technician in Professors Kuzyk's Nonlinear optical labs responsible for creating thin film samples and collecting data on self-healing properties of polymers after photo-degradation.

\section{Education}

Date: August 2009 to December 2013\\
University: Washington State University\\
Description: Graduated with a Bachelors in Physics with an option in Astrophysics and a minor in Mathematics.


\end{document} 